\LARGE \bf Eye-Tracking: a New Look at Human-Robot Interaction Assessment

### 2014-10-02 paper.tex
Experiment from introduction removed

Our working hypothesis is that with careful mapping between the LED
visualisations and the behaviour of the robot we can induce the understanding of
the functionality of the robot very easily. We propose to use the gaze data to
verify this hypothesis. With eye-tracking data we can judge whether the mapping
between the behaviour and visual actuators is useful or not for the participants'
understanding.  Moreover, we hypothesise that the good performers will be able
to anticipate the robot's motion. Eye-tracking data can also be useful to verify
the anticipation hypothesis.

The experiment consists in two phases. The first phase is the observation phase
during which the participants watch the robot move and detect an obstacle in a
``playground''. The second phase requires the participants to interact with the
robot by placing an obstacle in its path to make it detect the obstacle before
reaching a certain target.  After each phase the participant explain the
behaviour of the robot. The sensor data was visualised through LEDs with three
visualisation conditions: {\sf TRUE} visualisation, {\sf RANDOM} visualisation and {\sf NONE}
visualisation. Through this experiment we investigate the following research
questions:

\begin{enumerate}
    \item Are there different gaze patterns for different levels of performance
during the interaction? Moreover, can we see any anticipation patterns
for the good performers?

    \item How does displaying the sensor information on the robot' body as a
visual cue affects the gaze and performance of the participants?
\end{enumerate}

The rest of the paper is organised as follows. The second section gives
a brief review of the eye-tracking research done to quantify the
expertise and performance. The third section presents the specificities
of the study. The fourth section lists the main results. The fifth
section discusses the results. Finally, the sixth section concludes the
paper.

>>>>

%Our working hypothesis is that with careful mapping between the LED
%visualisations and the behaviour of the robot we can induce the understanding of
%the functionality of the robot very easily. We propose to use the gaze data to
%verify this hypothesis. With eye-tracking data we can judge whether the mapping
%between the behaviour and visual actuators is useful or not for the participants'
%understanding.  Moreover, we hypothesise that the good performers will be able
%to anticipate the robot's motion. Eye-tracking data can also be useful to verify
%the anticipation hypothesis.
%
%The experiment consists in two phases. The first phase is the observation phase
%during which the participants watch the robot move and detect an obstacle in a
%``playground''. The second phase requires the participants to interact with the
%robot by placing an obstacle in its path to make it detect the obstacle before
%reaching a certain target.  After each phase the participant explain the
%behaviour of the robot. The sensor data was visualised through LEDs with three
%visualisation conditions: {\sf TRUE} visualisation, {\sf RANDOM} visualisation and {\sf NONE}
%visualisation. Through this experiment we investigate the following research
%questions:
%
%\begin{enumerate}
%    \item Are there different gaze patterns for different levels of performance
%during the interaction? Moreover, can we see any anticipation patterns
%for the good performers?
%
%    \item How does displaying the sensor information on the robot' body as a
%visual cue affects the gaze and performance of the participants?
%\end{enumerate}
%
%The rest of the paper is organised as follows. The second section gives
%a brief review of the eye-tracking research done to quantify the
%expertise and performance. The third section presents the specificities
%of the study. The fourth section lists the main results. The fifth
%section discusses the results. Finally, the sixth section concludes the
%paper.
